Adaptive broadcast tree for multicores

### 2013-05-02 paper.tex
Moved the barrier ideas to a different section and added some more content

The coordinator knows how many of its slaves need to enter the
barrier. It can then just aggregate local barrier\_enters calls and
only communicate this information to the others once all children are
ready. Local communication can be shared-memory based, while global
communication should probably rather be message-passing based.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Barriers}

The idea is to explore barrier implementations. The idea is to
leverage information about the NUMA topology for better performance of
barrier intensive workloads. Every NUMA node has a coordinator node,
that knows how many threads on that node want to enter the
barrier. There is only local communication (possibly using a
share-memory implementation to exploit the shared cache) until the
point where all NUMA local threads did enter the barrier.  Then there
is ``global'' communication with other coordinators on other nodes
using a message-passing based algorithm. We believe that this scales
better than pure shared-memory implementations due to less
interconnect contention.
